Make any stupid plot you want

### 2021-02-19 draft/sections/implementation.tex
intro, circles many circles
tables/

\begin{document}
%what, why, how
\section{Prototype Implementation: Matplottoy}
\label{sec:implementation}
\begin{figure}[H]
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=\textwidth]{figures/code/scatter_0.png}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=\textwidth]{figures/code/line_1.png}
    \end{subfigure}
    \caption{Scatter plot and line plot implemented using prototype artists and data models, building on Matplotlib rendering.}
    \label{fig:code_scatter_line}
\end{figure}

@@

\begin{multicols*}{2}
\begin{minted}{python}
    fig, ax = plt.subplots()
    artist = Point(data, transforms)
    ax.add_artist(artist)
\end{minted}
\columnbreak
\begin{minted}{python}
    fig, ax = plt.subplots()
    artist = Line(data, transforms)
    ax.add_artist(artist)
\end{minted}
\end{multicols*}

We then add the \vartisteq=\mintinline{python}{Point} and  \vartisteq=\mintinline{python}{Line} artists that construct the scatter and line graphics. The arguments to the artist are the data \dtotal=\mintinline{python}{data} that is to be plotted and the aesthetic configuration \vchannel=\mintinline{python}{transforms}. We implement the artists as equivalence classes \vartisteq\ because it would be impractical to implement a new artist for every aesthetic setting, such as one artist for red lines and another for green.

@@

\begin{minted}{python}
class FiberBundle:
    def __init__(self, base, fiber):
        """
        base:  {'tables': ['vertex', 'edge', 'face']}
        fiber: {'component name': {'type':, 'monoid':,  'range':}}
        """
        self.base = base
        self.fiber = fiber

    def is_section(self, section):
        """checks if a section is from a given fiber bundle:
        are values in F, are keys in K"""
\end{minted}

>>>>

\begin{document}
\section{Prototype Implementation: Matplottoy}
\label{sec:implementation}
\begin{figure}[H]
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=\textwidth]{figures/code/scatter_0.png}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=\textwidth]{figures/code/line_1.png}
    \end{subfigure}
    \caption{Scatter plot and line plot implemented using prototype artists and data models, building on Matplotlib rendering.}
    \label{fig:code_scatter_line}
\end{figure}

@@

\begin{multicols*}{2}
\begin{minted}{python}
    fig, ax = plt.subplots()
    artist = Point(data, transforms)
    ax.add_artist(artist)
\end{minted}
\columnbreak
\begin{minted}{python}
    fig, ax = plt.subplots()
    artist = Line(data, transforms)
    ax.add_artist(artist)
\end{minted}
\end{multicols*}
We then add the \mintinline{python}{Point} and \mintinline{python}{Line} artists that construct the scatter and line graphics. The arguments to the artist are the data \mintinline{python}{data} that is to be plotted and the aesthetic configuration \mintinline{python}{transforms}. In general, the way in which we implement the math is described as follows:
\begin{tabular}
    \begin{table}{|l|l|l|}
        \hline
        \textbf{Math} & \texbf{Code} & \textbf{Examples} \\
        \textbf{\vartistEQ} & & \\

    \end{table}

\end{tabular}

\begin{mdframed}[roundcorner=10pt, frametitle= topology driven architecture, frametitlerule=true, frametitlebackgroundcolor=gray!10]
    \begin{description}
        \item[\textbf{\vartistEQ}] artist objects such as  \mintinline{python}{Point},  \mintinline{python}{Line}, \mintinline{python}{bar}
        \item[\textbf{\vchannel}] 
        \item[\textbf{\markd}] 
        \item[\textbf{\vtotal}] 
        \item[\textbf{\dtotal}] 
    \end{description}
\end{mdframed}
Implementing \gtotal\ and \gsection\ are out of scope for this prototype because they are part of the rendering process. We do not implement any form of \vindex\ because the scatter, line, and bar plots prototyped here directly broadcast from \dbasepoint to \gbasepoint, unlike for example an image which may need to be rotated. We implement the artists as equivalence classes \vartisteq\ because it would be impractical to implement a new artist for every aesthetic setting, such as one artist for red lines and another for green.

@@

\begin{minted}{python}
class FiberBundle:
    def __init__(self, base, fiber):
        """
        base:  {'tables': ['vertex', 'edge', 'face']}
        fiber: {'component name': {'type':, 'monoid':,  'range':}}
        """
        self.base = base
        self.fiber = fiber
\end{minted}
